### 2025-09-29 README.Rmd
Refrence contributor guidelines in README
addresses JOSS reviewer feedback #1

>>>>

## Contributor Guidelines

For issues, bug reports, and feature requests, [file a GitHub issue](https://github.com/rimonim/embedplyr/issues). For support or other inquiries, feel free to contact the maintainer by email at [info@ds4psych.com](mailto:info@ds4psych.com). However, the best way to get something changed is to do it yourself. We welcome contributions! See the [contributor guidelines](https://github.com/rimonim/embedplyr/wiki/Contributor-Guidelines) for details.
